Quantum Hoare Type Theory

### 2020-10-01 ms-paper/ms-paper.tex
Add note about Unruh's QHL work

\paragraph{Quantum Assertion Logic} An obvious need is to come up with an assertion logic similar to Separation Logic~\cite{reynolds2002} for quantum computing so as to be able to reason about only the interesting portions of the quantum state while still ensuring correctness of non-local effects such as entanglement. Various Quantum Hoare Logics that exist~\cite{ying_floydhoare_2012} currently do not support frame rules that provide Separation Logic its power.

>>>>

\paragraph{Quantum Assertion Logic} An obvious need is to come up with an assertion logic similar to Separation Logic~\cite{reynolds2002} for quantum computing so as to be able to reason about only the interesting portions of the quantum state while still ensuring correctness of non-local effects such as entanglement. Various Quantum Hoare Logics that exist~\cite{ying_floydhoare_2012} currently do not support frame rules that provide Separation Logic its power. The closest approach is that taken by \citet{unruh2019} that allows assertions on quantum state similar to what we would like in our setting, such as whether certain qubits are in classical state, or in uniform superposition, entangled or separable. We hope to incorporate these ideas in this work; this may require us to use a subspace semantics for the quantum state as shown in \citet{unruh2019}.
